---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

## Overview

Flexible and user-friendly probabilistic **segmentation** of time series with 
smooth and/or abrupt **regime changes** by a **mixture model-based** regression approach 
with a hidden logistic process, fitted by the EM algorithm.

## Installation

You can install the RHLP package from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/RHLP")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/RHLP", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("RHLP")
```

## Usage

```{r, message = FALSE}
library(RHLP)

data("toydataset")

K <- 5 # Number of regimes (mixture components)
p <- 3 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter = 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

rhlp <- emRHLP(toydataset$x, toydataset$y, K, p, q, 
                   variance_type, n_tries, max_iter, threshold, verbose, verbose_IRLS)

rhlp$summary()

rhlp$plot()
```
