---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

# Overview

Flexible and user-friendly probabilistic **segmentation** of time series with 
smooth and/or abrupt **regime changes** by a **mixture model-based** regression
approach with a hidden logistic process, fitted by the EM algorithm.

# Installation

You can install the RHLP package from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/RHLP")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/RHLP", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("RHLP")
```

# Usage

```{r, message = FALSE}
library(RHLP)
```

```{r, echo = TRUE}
# Application to a toy data set
data("toydataset")
x <- toydataset$x
y <- toydataset$y

K <- 5 # Number of regimes (mixture components)
p <- 3 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter = 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

rhlp <- emRHLP(X = x, Y = y, K, p, q, variance_type, n_tries, 
               max_iter, threshold, verbose, verbose_IRLS)

rhlp$summary()

rhlp$plot()
```

```{r, echo = TRUE}
# Application to a real data set
data("realdataset")
x <- realdataset$x
y <- realdataset$y2

K <- 5 # Number of regimes (mixture components)
p <- 3 # Dimension of beta (order of the polynomial regressors)
q <- 1 # Dimension of w (order of the logistic regression: to be set to 1 for segmentation)
variance_type <- "heteroskedastic" # "heteroskedastic" or "homoskedastic" model

n_tries <- 1
max_iter = 1500
threshold <- 1e-6
verbose <- TRUE
verbose_IRLS <- FALSE

rhlp <- emRHLP(X = x, Y = y, K, p, q, variance_type, n_tries, 
               max_iter, threshold, verbose, verbose_IRLS)

rhlp$summary()

rhlp$plot()
```

# Model selection

In this package, it is possible to select models based on information criteria 
such as **BIC**, **AIC** and **ICL**.

The selection can be done for the two following parameters:

 * **K**: The number of regimes;
 * **p**: The order of the polynomial regression.

Let's select a RHLP model for the following time series **Y**:

```{r, message = FALSE}
data("toydataset")
x <- toydataset$x
y <- toydataset$y

plot(x, y, type = "l", xlab = "x", ylab = "Y")
```

```{r, message = FALSE}
selectedrhlp <- selectRHLP(X = x, Y = y, Kmin = 2, Kmax = 6, pmin = 0, pmax = 3)

selectedrhlp$plot(what = "estimatedsignal")
```
